Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
we found T=372 ms to be optimal in DCASE 2016
typo section Vii.B, ob-a => ob-c
Reintroduce commits d56dd7..b1645a

\subsubsection*{Early \vs late integration}
Late integration, \ie building a prediction by majority voting over $128$ local windows of duration $T=372\,\mathrm{ms}$, outperforms early integration, \ie classifying the acoustic scene with a global window of duration $T=24\,\mathrm{s}$.
This result suggests that, despite its discriminative power at fine scales, the scattering transform is unable to segregate distinct acoustic events beyond the scale of about one second.
Therefore, it is beneficial to regard the scattering transform as a mid-level descriptor of acoustic content, not as a high-level descriptor, and adopt a data-driven strategy for the temporal integration of acoustic events within one scene.
Surprisingly, although we ran an extensive number of experiments to formulate object-based clustering into a supervised setting for acoustic scene classification, none of them managed to outperform the baseline strategy in temporal integration, namely majority voting. The best result was achieved by the \emph{ob-a} approach using log-compressed scattering, and was of 66\% (0.7).

@@

Our results on the development dataset are reported in Table \ref{table:dcase2016}, in comparison with a baseline of MFCCs coefficients and a generative classifier, namely Gaussian mixture models with $16$ Gaussians per model. The baseline relies on a late integration scheme, wherein the reduction function $\rho$ is a product of likelihoods.
The average accuracy across classes is brought from $70.8\%$ to $79.4\%$.
The results on the evaluation dataset are awaiting publication by the DCASE organizing committee, and will be disclosed in August 2016.

>>>>

\subsubsection*{Early \vs late integration}
Late integration, \ie building a prediction by majority voting over $128$ local windows of duration $T=372\,\mathrm{ms}$, outperforms early integration, \ie classifying the acoustic scene with a global window of duration $T=24\,\mathrm{s}$.
This result suggests that, despite its discriminative power at fine scales, the scattering transform is unable to segregate distinct acoustic events beyond the scale of about one second.
Therefore, it is beneficial to regard the scattering transform as a mid-level descriptor of acoustic content, not as a high-level descriptor, and adopt a data-driven strategy for the temporal integration of acoustic events within one scene.
Surprisingly, although we ran an extensive number of experiments to formulate object-based clustering into a supervised setting for acoustic scene classification, none of them managed to outperform the baseline strategy in temporal integration, namely majority voting. The best result was achieved by the \emph{ob-c} approach using log-compressed scattering, and was of 66\% (0.7).

@@

Our results on the development dataset are reported in Table \ref{table:dcase2016}, in comparison with a baseline of MFCCs coefficients and a generative classifier, namely Gaussian mixture models with $16$ Gaussians per model. The baseline relies on a late integration scheme, wherein the reduction function $\rho$ is a product of likelihoods.
The average accuracy across classes is brought from $70.8\%$ to $79.4\%$.
Furthermore, our cross-validation analyses confirmed that the value $T=372\,\mathrm{ms}$ for the support of the low-pass filter $\boldsymbol{\phi}(t)$ is optimal when applying late integration by majority voting.
The results on the evaluation dataset are awaiting publication by the DCASE organizing committee, and will be disclosed in August 2016.
